Guidelines for Designing Touch Interfaces for Controlling Robotic Nozzles in Critical Emergency Situations. \thanks{wtf}

### 2015-09-22 Outline.tex
Continued working on Outline, milestone before annotations

\section{Introduction}
Here goes text. Write about Purpose, Motivation, Contents and Resources.

\begin{description}
	\item[Purpose of the paper] Well, explain the purpose of the paper.
	\item[Motivation for the paper] Make clear why this paper needs to be done.
	\item[Content] The final paper will include...
	\item[Resources] Resources I we plan to use in the work of this paper.
\end{description}

@@

\subsection{Design of an A/B test}
In order to test if increased color contrast in a touch interface can completedly remove all faulty interactions an A/B test was conducted.
\emph{This section will contain a short but descriptive text about how the A/B test was prepared, built and performed. It will describe who participated}.

@@

\section{Result}
All results produced from these tests are here presented with clear numbers

\subsection{A/B test}
text about a/b test results

\subsection{Evaluation}
text about the results that came out of the evaluation.

@@

\subsection{Conclusions and Guidelines}
Here we'll present our conclusions based on the resulting outcome from the tests. We'll also present our four guidelines on how to design a touch interface compatible for emergency situations. These guidlines will be created based on the test results.

@@

\subsection{Future Work}
Due to the limited time we have on this paper there will be alot of things that can be improved. We'll in this section give our suggestions on things that could be done in future or continued work.

>>>>

\section{Introduction}
Introduction part will contain a purpose of the paper and a motivation for why the paper was made.

\begin{description}
	\item[Purpose of the paper] Can a well designed touch interface for controlling robotic nozzles reach a level of zero faulty interactions in critical emergency situations by increasing the color contrast of the interface?
	\item[Motivation for the paper] In critical emergency situations, like in the case of fire, a graphical touch user interface should not be the weak link on getting the job done when controlling robotic nozzles. One single press on the wrong button can be the difference between life or death.
\end{description}

@@

\subsection{Design of an A/B test}
In order to test if increased color contrast in a touch interface can completely remove all faulty interactions an A/B test was conducted.
\emph{This section will contain a short but descriptive text about how the A/B test was prepared, built and performed. It will describe who participated}.

@@

\section{Result}
All results produced from the tests are here presented with clear numbers and conclusions.

\subsection{Evaluation}
The evaluation itself and a text about the evaluation results.

@@

\subsection{Conclusions and Guidelines}
Here we'll present our conclusions based on the resulting outcome from the tests. We'll also present our four guidelines on how to design a touch interface compatible for emergency situations. These guidelines will be created based on the test results.

@@

\subsection{Future Work}
Due to the limited time we have on this paper there will be a lot of things that can be improved. We'll in this section give our suggestions on things that could be done in future or continued work.
